---
title: "FamilyApp for Child's Height Predection"
author: "Abdou K. Allayeh"
date: "23 September2020"
output: slidy_presentation
---


#ShinyApp presentation project

This project consists of two parts. First, we will create a Shiny application and deploy it on Rstudio's servers. Second, we will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application.

- Links
- URL for running App https://drallayeh.shinyapps.io/Family/?_ga=2.139174003.1769456352.1600785220-996303787.1600785220
- URL for github site
https://github.com/drallayeh/Genomics/tree/master/Family/Family

- URL for Presentation
https://rpubs.com/drallayeh/664910

# The data used in the app comes from the GaltonFamilies dataset. 

```{r}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

# Plot
In the scatterplot below are represented the data used for the prediction model

```{r plot}
library(HistData)
data(GaltonFamilies)
plot(jitter(GaltonFamilies$childHeight) ~ GaltonFamilies$midparentHeight,xlab="Average Height of the Parents (in inches)",ylab="Height of the Child (in inches)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "pink", "light blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.8)
```





# ThankYou